\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Try to find more aacurrate model
Added Figure 18 title

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "(a) The $10\\text{-}D$ model error for tSNE layout in $\\gD{}$ of the MNIST digit 1 dataset. Most low model errors are distributed along the big non-linear clutser, while most large model errors are concentrated along the small cluster. (b) There are certain images that exhibit large errors due to their deviation from the non-linear cluster, which makes them anomalies. The images associated with large model errors shows different patterns of digit 1."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
#| out-height: 80%

>>>>

benchmark_mnist <- 0.1

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in layout a of the MNIST digit 1 dataset show a pattern. Most low model errors are distributed along the big non-linear clutser, while most large model errors are distributed along the small cluster. Along the non-linear cluster, the angle of digit 1 changes. Some images have large errors due to their deviation from the non-linear cluster, which makes them anomalies. The images associated with large model errors shows different patterns of digit 1."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
#| out-height: 80%

### 2024-09-25 paper.tex
Updated Figure 15 title with more precise description
Added Figure 18 title

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows three clusters with
two of them being close and one separated from the others. This is why
b1, b2, and b3 shows a connected edge between the close clusters, as
proven by Figure~\ref{fig-pbmc-mse} as a best layout. Viewing the fitted
model in \(9\text{-}D\), helps to see some unobserved patterns of the
data: (i) dense points, and (ii) non-linear clusters. Videos of the
langevitour animations for the models are available at
\url{https://youtu.be/0cKX_HG_n0k} and
\url{https://youtu.be/KhJvsRtaX04} respectively.}

@@

\caption{\label{fig-model-error-mnist}(a) The \(10\text{-}D\) model
error for tSNE layout in \(\gD{}\) of the MNIST digit 1 dataset. Most
low model errors are distributed along the big non-linear clutser, while
most large model errors are concentrated along the small cluster. (b)
There are certain images that exhibit large errors due to their
deviation from the non-linear cluster, which makes them anomalies. The
images associated with large model errors shows different patterns of
digit 1.}

>>>>

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows three clusters with
two of them being close and one separated from the others. This is why
b1, b2, and b3 shows a connected edge between the close clusters, as
proven by Figure~\ref{fig-pbmc-mse} as a reasonable layout. Viewing the
fitted model in \(9\text{-}D\), helps to see some unobserved patterns of
the data: (i) dense points, and (ii) non-linear clusters. Videos of the
langevitour animations for the models are available at
\url{https://youtu.be/0cKX_HG_n0k} and
\url{https://youtu.be/KhJvsRtaX04} respectively.}

@@

\caption{\label{fig-model-error-mnist}The \(10\text{-}D\) model error in
layout a of the MNIST digit 1 dataset show a pattern. Most low model
errors are distributed along the big non-linear clutser, while most
large model errors are distributed along the small cluster. Along the
non-linear cluster, the angle of digit 1 changes. Some images have large
errors due to their deviation from the non-linear cluster, which makes
them anomalies. The images associated with large model errors shows
different patterns of digit 1.}
